04_DESeq_sexes

### 2019-08-28 analysis/04_DESeq2_sexes.Rmd
now with updated plots
clea up

library(tidyverse)
library(DESeq2)
library(cowplot)
library(RColorBrewer)
library(pheatmap)
library(kableExtra)
library(viridis)
library(forcats)
library("wesanderson")
library(caret) # LDA analysis
library(MASS) # LDA analysis

library("BiocParallel")
register(MulticoreParam(4))

@@

knitr::opts_chunk$set(fig.path = '../figures/sexes/', cache = TRUE)
```

@@

# drop columsn that are bad for model
c.colData$bird <- NULL
c.colData$tissue <- NULL
c.colData$study <- NULL
c.colData$group <- NULL
head(c.colData)
```

@@

@@

gonPCA <- returnPCAs2(dds.gonad)
plotPC12(gonPCA, "Gonad")
```

>>>>

library(tidyverse)
library(DESeq2)
library(cowplot)
library(pheatmap)
library(viridis)
library(forcats)
library(caret) # LDA analysis
library(MASS) # LDA analysis

library(BiocParallel)
register(MulticoreParam(6))

@@

knitr::opts_chunk$set(fig.path = '../figures/sexes/', cache = TRUE,  message=F, comment=FALSE, warning=FALSE)
```

@@

# drop columsn that are bad for model AND not needed for later joining
c.colData$bird <- NULL
c.colData$tissue <- NULL
c.colData$study <- NULL
c.colData$group <- NULL
head(c.colData)
```

@@

## Variance stabilized data

```{r vsd}

@@

gonPCA <- returnPCAs2(dds.gonad)
plotPC12(gonPCA, "Gonad")
